Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-31 ijar-npb-ms.tex
My acknowledgements
minor tweaks in section 6 and computation of bounds in separate subsection

The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
is extended to incorporate the sets of priors approach of \citet{2009:WalterAugustin},
enabling diagnosis of prior-data conflict which is consequential at the system
level, via sets of system reliability functions.

@@

If $\frac{s}{N + m - 1} < y < \frac{s + m - 1}{N + m - 1}$ then 
Theorem 2 cannot determine stochastic dominance.  The following Lemma which is slightly
more computationally costly, but still much faster than an exhaustive search, may be able to determine first-order
stochastic dominance in such situations.
\begin{lemma}
  \label{lem:n}
  Let $\beta_n$ denote the Beta-Binomial distribution as in Theorem \ref{thm:n}.  Define
  \[ \mathcal{L}_{\nu,\nl}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)} \]
  Then,
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \le 1 \\
       \mathcal{L}_{\nu,\nl}(m) \ge 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \ge 1 \\
       \mathcal{L}_{\nu,\nl}(m) \le 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{lemma}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n2}.
In the cases where neither Theorem \ref{thm:n} or Lemma \ref{lem:n} apply,
the entire posterior system reliability function must be optimised to 
find the minima/maxima.
In practise, in the examples to be presented in the sequel, Theorem 
\ref{thm:n} and Lemma \ref{lem:n} do provide guarantees of first-order
stochastic dominance for the vast majority of time points, $t$,
substantially lowering the computational costs of performing the
minimisation/maximisation involved in finding the sets of system 
reliability functions compared to either numerical optimisation or
an exhaustive grid search (which would get exponentially slower in 
the number of different components).

@@

\subsection{Prior parameter choice}
In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We advocate that this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.

As mentioned in Section~\ref{sec:nonparamapproach}, the functioning probabilities $\ptk$
must satisfy $p^k_{t_j} \ge p^k_{t_{j+1}}$.% (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
%***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
%as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
%but does this need to hold for the prior guess range bound $\yktzu$?)***
This naturally translates to conditions on the prior for $\ptk$,
so that for example 
$\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$ should hold.
Because $s^k_t/n_k$ is decreasing in $t$, the weighted average property of the update step in
equation \eqref{eq:nyupdate} for $\ykt$ ensures that 
$\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
In situations where one has a high degree of certainty about the functioning probability for low $t$,
but less certainty about what happens for larger $t$,
then one can let $\yktzl$ drop to (almost) 0, but clearly $\yktzu$ should not increase.
%***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
%If we know, e.g., pretty much what's going on for low $t$
%but want to be much more cautious for high $t$,
%then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.

@@

%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
%to get proper posteriors***
As mentioned in Section~\ref{sec:setsofbetapriors},
it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
this can lead to improper posterior predictive distributions.
%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
However, it is possible to choose values close to $0$ and $1$, respectively,
and due to the linear update step for $\yktn$ (see Equation~\eqref{eq:nyupdate}),
posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
%***what to do in extreme tail of component distributions?
%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
Likewise, our nonparametric method does not cause unintuitive tail behaviour
as some parametric methods do;
there is no problem, for example, with assigning $\yktnu$ near-zero for high $t$ if prior knowledge suggests so.

@@

>>>>

The elements reviewed and extended above culminate hereinafter in the primary contribution of the current work,
providing a framework in which the nonparametric Bayesian system reliability approach developed in \cite{2015:bayessurvsign}
is extended to sets of system reliability functions
by incorporating the sets of priors approach of \citet{2009:WalterAugustin}.
This allows for partial or vague specification of prior component reliability functions,
and enables diagnosis of prior-data conflict which is consequential at the system level.

\subsection{Computation of bounds}

@@

If $\frac{s}{N + m - 1} < y < \frac{s + m - 1}{N + m - 1}$ then 
Theorem 2 cannot determine stochastic dominance.  The following Lemma which is slightly
more computationally costly, but still much faster than an exhaustive search, may be able to determine first-order
stochastic dominance in such situations.
\begin{lemma}
  \label{lem:n}
  Let $\beta_n$ denote the Beta-Binomial distribution as in Theorem \ref{thm:n}.  Define
  \[ \mathcal{L}_{\nu,\nl}(l) := \frac{p(l \mid y, \nu, m, s, N)}{p(l \mid y, \nl, m, s, N)} \]
  Then,
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \le 1 \\
       \mathcal{L}_{\nu,\nl}(m) \ge 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \ge_{\mathrm{st}} \beta_{\nl} \]
  and
  \[ \left. \begin{aligned}
       \mathcal{L}_{\nu,\nl}(0) \ge 1 \\
       \mathcal{L}_{\nu,\nl}(m) \le 1 \\
    \end{aligned} \right\}
    \implies \beta_{\nu} \le_{\mathrm{st}} \beta_{\nl} \]
\end{lemma}
The proof is provided in Appendix \ref{ap:proofs}, p.\pageref{prf:n2}.
In the cases where neither Theorem \ref{thm:n} or Lemma \ref{lem:n} apply,
the entire posterior system reliability function must be optimised to 
find the minima/maxima.
In practice, in the examples to be presented in the sequel, Theorem 
\ref{thm:n} and Lemma \ref{lem:n} do provide guarantees of first-order
stochastic dominance for the vast majority of time points, $t$,
substantially lowering the computational costs of performing the
minimisation/maximisation involved in finding the sets of system 
reliability functions compared to either numerical optimisation or
an exhaustive grid search (which would get exponentially slower in 
the number of different components).

@@

\subsection{Prior parameter choice}

In the following, we will give some guidelines on how to choose the parameter sets $\PkZi{1}, \ldots, \PkZi{\tmax}$
which define the set of prior discrete reliability functions for components of type $k$.
We advocate that this is much easier in terms of $\nz$ and $\yz$ than it would be in terms of $\alpha$ and $\beta$.

As mentioned in Section~\ref{sec:nonparamapproach}, the functioning probabilities $\ptk$
must satisfy $p^k_{t_j} \ge p^k_{t_{j+1}}$.% (***or $p^k_{t_i} \ge p^k_{t_i}$ for all $i < j$).
%***not necessary to ensure $p^k_{t_j} \ge p^k_{t_{j+1}}$ via $\yzl_{k,t_j} \ge \yzu_{k,t_{j+1}}$
%as for relatively dense $t$ grids, neighbouring intervals should be able to overlap***
%(Prior guess for $p^k_t$ interpretation would say that $\yktz$ cannot increase,
%but does this need to hold for the prior guess range bound $\yktzu$?)***
This naturally translates to conditions on the prior for $\ptk$,
so that for example 
$\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$ should hold.
Because $s^k_t/n_k$ is decreasing in $t$, the weighted average property of the update step in
Equation \eqref{eq:nyupdate} for $\ykt$ ensures that 
$\ynu_{k,t_j} \ge \ynu_{k,t_{j+1}}$ and $\ynl_{k,t_j} \ge \ynl_{k,t_{j+1}}$.
In situations where one has a high degree of certainty about the functioning probability for low $t$,
but less certainty about what happens for larger $t$,
then one can let $\yktzl$ drop to (almost) 0, but clearly $\yktzu$ should not increase.
%***Require $\yzu_{k,t_j} \ge \yzu_{k,t_{j+1}}$ and $\yzl_{k,t_j} \ge \yzl_{k,t_{j+1}}$.
%If we know, e.g., pretty much what's going on for low $t$
%but want to be much more cautious for high $t$,
%then $\yktzl$ can drop to 0, but $\yktzu$ cannot increase.

@@

%***generally require $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$
%to get proper posteriors***
As mentioned in Section~\ref{sec:setsofbetapriors},
it is not advisable to choose $\yktzl = 0$ and $\yktzu = 1$.
For any $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$,
this can lead to improper posterior predictive distributions.
%Generally, one should choose $\yktzl > 0$ and $\yktzu < 1$ for all $t \not\in \big(\min(\vec{t}^k), \max(\vec{t}^k)\big)$.
However, it is possible to choose values close to $0$ and $1$, respectively,
and due to the linear update step \eqref{eq:nyupdate} for $\yktn$,
posterior inferences are not overly sensitive to whether $\yktnu = 0.99$ or $\yktnu = 0.9999$.
%***what to do in extreme tail of component distributions?
%How sensitive is the method to choosing prior (lower, upper) mean near-zero (how near?) for $p^k_t$ at high $t$'s?***
Likewise, our nonparametric method does not cause unintuitive tail behaviour
as some parametric methods do;
there is no problem, for example, with assigning $\yktnu$ near-zero for large $t$ if prior knowledge suggests so.

@@

\section*{Acknowledgements}

Louis Aslett was supported by the i-like project (EPSRC grant reference number EP/K014463/1).
